Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2017-06-09 reports/Effects_of_AWD_N_on_SB.rmd
Update title per Ole's change

---
title: "Do Alternate Wetting and Drying Irrigation Technologies and Nitrogen Rates Affect Rice Sheath Blight?"
thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Adam.Sparks@usq.edu.au"
author:
  - A.H. Sparks and N.P. Castilla and B.O. Sander
keywords: "_Rhizoctonia solani_, Irrigation"
abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second and third authors: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
  html_document: default
csl: phytopathology.csl
bibliography: AWD_N_ShB.bib
---

>>>>

---
title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Adam.Sparks@usq.edu.au"
author:
  - A.H. Sparks and N.P. Castilla and B.O. Sander
keywords: "_Rhizoctonia solani_, Irrigation"
abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second and third authors: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
  html_document: default
csl: phytopathology.csl
bibliography: AWD_N_ShB.bib
---
